The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-04-14 paper.tex
update subsection{Relative Landmark Positions}

>>>>

A relative position of a landmark regarding a reference object can be described using the ANNO. 
For this, the corresponding landmark (the subject), a reference object 
(anatomical structure, anatomical axis, anatomical plane or another landmark) and, if required, an anatomical direction 
(in relation to the reference object) must be specified. If the direction was not specified, the landmark is located on the reference object.
